---
title: "QBS 122 Social Network Analysis Project"
author: "Connolly Carroll"
date: "5/29/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd('/Users/connollycarroll/Desktop/Q3/122')
```

```{r, results='hide'}
library(sna)
library(statnet)
library(coda)
library(dplyr)
library(tidyverse)
library(latentnet)
library(amen)
library(eigenmodel)
par(mfrow=c(1,1))
```

Load edges and nodes.
```{r, results='hide'}
s1 = read.csv('got_dat/data/got-s1-edges.csv')
s2 = read.csv('got_dat/data/got-s2-edges.csv')
s3 = read.csv('got_dat/data/got-s3-edges.csv')
s4 = read.csv('got_dat/data/got-s4-edges.csv')
s5 = read.csv('got_dat/data/got-s5-edges.csv')
s6 = read.csv('got_dat/data/got-s6-edges.csv')
s7 = read.csv('got_dat/data/got-s7-edges.csv')
s8 = read.csv('got_dat/data/got-s8-edges.csv')

s1n = read.csv('got_dat/data/got-s1-nodes.csv')
s2n = read.csv('got_dat/data/got-s2-nodes.csv')
s3n = read.csv('got_dat/data/got-s3-nodes.csv')
s4n = read.csv('got_dat/data/got-s4-nodes.csv')
s5n = read.csv('got_dat/data/got-s5-nodes.csv')
s6n = read.csv('got_dat/data/got-s6-nodes.csv')
s7n = read.csv('got_dat/data/got-s7-nodes.csv')
s8n = read.csv('got_dat/data/got-s8-nodes.csv')
```

Consolidate all edges into one data frame based on unique pairs of actors, summing interactions. Look for overlap between unique nodes and names in death df, assign status of dead or alive accordingly. Assign house based on parsing ID for last name in ID. Final df: all actor interactions throughout the show, final alive status, house (surname).
```{r, results='hide'}
df <- rbind(s1, s2, s3, s4, s5, s6, s7, s8)

df$unique_pair_tag <- rep(NaN, nrow(df))

for (i in 1:nrow(df)){
  alpha_set <- sort(c(df$Source[i], df$Target[i]))
  tag_int <- paste(alpha_set[1], alpha_set[2], sep = '')
  
  df$unique_pair_tag[i] <- tag_int
}
```

Compile unique list of nodes and associated IDs. I have first names with first letter capitalized here.
```{r, results='hide'}
nodes_df <- rbind(s1n, s2n, s3n, s4n, s5n, s6n, s7n, s8n)
nodes_df <- nodes_df[-62, ]
nodes_df <- distinct(nodes_df, nodes_df$Id, .keep_all = TRUE)
nodes_df <- select(nodes_df, -3)

for (i in 1:nrow(nodes_df)){
  if (nodes_df$Id[i] %in% df$Source | nodes_df$Id[i] %in% df$Target){
  }
  else{
    nodes_df <- nodes_df[-i, ]
  }
}
```

Check for reasonable results. All frequencies range between 1 and 8, the number of seasons over which data is compiled.
```{r, results='hide'}
aa <- as.data.frame(table(df$unique_pair_tag))
# (aa)
# (table(aa$Freq))
```

Create a table with summed interactions by unique pair tag.
```{r, results='hide'}
df_counts <- df %>%
  group_by(df$unique_pair_tag) %>%
  summarize_at(vars(Weight), sum, na.rm = TRUE)
```

Grab data from summed interactions table and add to main df.
```{r, results='hide'}
df$final_counts1 <- rep(NaN, nrow(df))
for (i in 1:nrow(df)){
  tag_int <- df$unique_pair_tag[i]
  df$final_counts1[i] <- df_counts[df_counts['df$unique_pair_tag'] == tag_int, 'Weight']
}
```

```{r, results='hide'}
df$final_counts <- rep(NaN, nrow(df))
for (i in 1:nrow(df)){
  df$final_counts[i] <- df[i, 'final_counts1'][[1]]
}

df <- select(df, -6)
```

Subset for unique pairs of actors with summed interactions.
```{r, results='hide'}
edges_df <- distinct(df, df$unique_pair_tag, .keep_all = TRUE)
edges_df <- select(edges_df, -3, -4, -7)
edges_df$weight <- edges_df$final_counts/100
edges_df <- edges_df[, c(1, 2, 5, 3, 4)]
```

Get first name tags for each actor in the deaths df. Extract first name with first letter capitalized.
```{r, results='hide'}
char_det <- read.csv('game_of_thrones_deaths.csv')
int_df <- select(char_det, name)
int_df$first_name <- rep(NaN, length(int_df))

for(i in 1:length(int_df$name)){
  int_df$first_name[i] <- strsplit(int_df$name[i], '\\s+')[[1]][1]}
```

Add alive or dead attribute. Change a few edge cases manually.
```{r, results='hide'}
nodes_df$Dead <- rep(NaN, nrow(nodes_df))
for (i in 1:nrow(nodes_df)){
  nodes_df$Dead[i] <- ifelse(nodes_df$Label[i] %in% int_df$first_name, 1, 0)
}

nodes_df[nodes_df$Label == 'Drogo', 'Dead'] <- 1
nodes_df[nodes_df$Label == 'Hugh of the Vale', 'Dead'] <- 1
nodes_df[nodes_df$Label == 'Hot Pie', 'Dead'] <- 1
nodes_df[nodes_df$Label == 'Khal Moro', 'Dead'] <- 1
nodes_df[nodes_df$Label == 'Silk King', 'Dead'] <- 1
nodes_df[nodes_df$Label == 'Spice King', 'Dead'] <- 1
nodes_df[nodes_df$Label == 'Night King', 'Dead'] <- 1
nodes_df[nodes_df$Label == 'Tickler', 'Dead'] <- 1
nodes_df[nodes_df$Label == 'High Septon', 'Dead'] <- 1
nodes_df[nodes_df$Label == 'High Sparrow', 'Dead'] <- 1
nodes_df[nodes_df$Label == 'Jon Arryn', 'Dead'] <- 1
nodes_df[nodes_df$Label == 'Aegon', 'Dead'] <- 1
nodes_df[nodes_df$Label == 'Rhaegar', 'Dead'] <- 1
nodes_df[nodes_df$Label == 'Jon', 'Dead'] <- 0
nodes_df[nodes_df$Label == 'Lyanna Mormont', 'Dead'] <- 1
nodes_df[nodes_df$Label == 'Theon', 'Dead'] <- 1
nodes_df[nodes_df$Label == 'Tyene', 'Dead'] <- 1
```

```{r, results='hide'}
nodes_df$num_ind <- as.numeric(rownames(nodes_df))
edges_df$NS <- rep(NaN, nrow(edges_df))
edges_df$NT <- rep(NaN, nrow(edges_df))
for(i in 1:nrow(edges_df)){
  edges_df$NS[i] <- nodes_df[nodes_df$Id == edges_df$Source[i], 'num_ind']
  edges_df$NT[i] <- nodes_df[nodes_df$Id == edges_df$Target[i], 'num_ind']
}
```

```{r, results='hide'}
mat <- matrix(0, 406, 406)
for(i in 1:406){
  mat[edges_df[i, 6], edges_df[i, 7]] <- edges_df[i, 3]
}
```

Display data graphically.
```{r fig1, fig.height = 4, fig.width = 4, fig.align = 'center'}
library(igraph)
nodes <- nodes_df$Id
gnet <- graph_from_data_frame(d = edges_df[, 1:2], vertices = nodes, directed = FALSE)
E(gnet)$weight <- edges_df$weight
plot(gnet, layout = layout.random,
     vertex.label.cex = 0.5,
     vertex.size = 3,
     vertex.label.color = 'black',
     edge.width = E(gnet)$weight,
     asp = 0)
```

Compute summary statistics with igraph.
```{r}
# (edge_density(gnet))
# (centr_degree(gnet)$centralization)
# (transitivity(gnet))
```

```{r}
deg1 <- degree(gnet)
str1 <- strength(gnet, weights = edges_df$weight)
btwn1 <- betweenness(gnet, weights = edges_df$weight)
close1 <- closeness(gnet, weights = edges_df$weight)
eigen1 <- eigen_centrality(gnet, weights = edges_df$weight)$vector

(var(deg1))
(var(str1))
(var(btwn1))
(var(close1))
(var(eigen1))
```

Compute summary statistics with sna.
```{r, results='hide'}
detach('package:igraph', unload = TRUE)
```

```{r}
pnet <- as.network(edges_df[, 1:3],
                 matrix.type = 'edgelist',
                 directed = FALSE,
                 ignore.eval = FALSE,
                 names.eval = 'weight')
```

Network: Density, centralization, transitivity (triad census)
```{r}
(gden(pnet, mode = 'graph', ignore.eval = FALSE))
(centralization(pnet, degree, mode = 'graph'))
(triad.census(pnet, mode = 'graph'))
(gtrans(pnet, mode = 'graph', measure = 'weak', use.adjacency = TRUE))
```

Node: degree, strength, closeness, betweenness, eigenvector, variance
```{r}
 deg2 <- degree(pnet, gmode = 'graph', cmode = 'undirected')
# 
# geo2 <- as.data.frame(geodist(pnet, inf.replace = 0)$gdist)
# geo2 <- cbind(geo2, means = rowSums(geo2)/405)
# 
# btwn2 <- betweenness(pnet, gmode = 'graph', cmode = 'undirected')
# 
# eigen2 <- evcent(pnet, gmode = 'graph', use.eigen = FALSE)
# 
# close2 <- closeness(plot(pnet))
# 
# (var(deg2))
# (var(geo2$means))
# (var(btwn2))
# (var(close2))
# (var(eigen2))
```

Choose most central actors to model, subset. Assortativity, don't have mutuality because undirected.
```{r, results='hide'}
deg_ls <- as.data.frame(cbind(seq(1, 406, 1), deg2))
deg_ls <- deg_ls[order(-deg_ls$deg2), ]

nodes_suba <- nodes_df[deg_ls[1:100, 'V1'], ]
```

```{r, results='hide'}
str_ls <- as.data.frame(cbind(seq(1, 406, 1),str1))
str_ls <- str_ls[order(-str_ls$str1), ]

nodes_subb <- nodes_df[str_ls[1:100, 'V1'], ]
```

```{r}
(nodes_suba[1:5, 'Id'])
(nodes_subb[1:5, 'Id'])
```

```{r, results='hide'}
nodes_subb$sex <- c(0, 0, 1, 1, 1, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 1, 1, 0, 0, 0, 1, 0, 0, 1, 1, 0, 1, 0, 0, 0, 0, 1, 0, 0, 1, 0, 1, 0, 0, 0, 0, 1, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 1, 0, 0, 1, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 0, 1, 0, 1, 0, 0, 0, 1, 0, 0, 1, 0, 0, 0, 0, 0)

nodes_subb$house <- rep('lightorange', 100)

nodes_subb <- nodes_subb[, c(1, 2, 4, 3, 5)]

nodes_subb$lannister <- rep(0, 100)
lann_mems <- c('Tyrion', 'Cersei', 'Jaime', 'Tywin', 'Lancel')
lkid <- c('Joffrey', 'Myrcella', 'Tommen')
lmar <- c('Robert', 'Margaery', 'Sansa')
nodes_subb[nodes_subb$Label %in% lann_mems, 'house'] <- 'yellow'
nodes_subb[nodes_subb$Label %in% lann_mems, 'lannister'] <- 1
nodes_subb[nodes_subb$Label %in% lkid, 'lannister'] <- 2
nodes_subb[nodes_subb$Label %in% lmar, 'lannister'] <- 3

nodes_subb$targaryen <- rep(0, 100)
targ_mems <- c('Daenerys', 'Viserys', 'Jon', 'Aemon')
tmar <- c('Drogo')
nodes_subb[nodes_subb$Label %in% targ_mems, 'targaryen'] <- 1
nodes_subb[nodes_subb$Label %in% targ_mems, 'house'] <- 'red'
nodes_subb[nodes_subb$Label %in% tmar, 'targaryen'] <- 3

nodes_subb$stark <- rep(0, 100)
stark_mems <- c('Sansa', 'Arya', 'Ned', 'Rickon', 'Robb', 'Benjen', 'Bran')
skid <- c('Jon')
smar <- c('Tyrion', 'Talisa', 'Ramsey', 'Catelyn')
nodes_subb[nodes_subb$Label %in% stark_mems, 'stark'] <- 1
nodes_subb[nodes_subb$Label %in% stark_mems, 'house'] <- 'blue'
nodes_subb[nodes_subb$Label %in% skid, 'stark'] <- 2
nodes_subb[nodes_subb$Label %in% smar, 'stark'] <- 3

nodes_subb$baratheon <- rep(0, 100)
bar_mems <- c('Joffrey', 'Myrcella', 'Tommen', 'Robert', 'Gendry', 'Renly', 'Stannis', 'Shireen')
bmar <- c('Cersei', 'Selyse', 'Margaery')
nodes_subb[nodes_subb$Label %in% bar_mems, 'baratheon'] <- 1
nodes_subb[nodes_subb$Label %in% bar_mems, 'house'] <- 'orange'
nodes_subb[nodes_subb$Label %in% bmar, 'baratheon'] <- 3

nodes_subb$tyrell <- rep(0, 100)
tyr_mems <- c('Margaery', 'Olenna', 'Mace', 'Loras')
tymar <- c('Renly', 'Jeoffrey', 'Tommen')
nodes_subb[nodes_subb$Label %in% tyr_mems, 'tyrell'] <- 1
nodes_subb[nodes_subb$Label %in% tyr_mems, 'house'] <- 'lightgreen'
nodes_subb[nodes_subb$Label %in% tymar, 'tyrell'] <- 3

nodes_subb$arryn <- rep(0, 100)
arryn_mems <- c('Robin')
amar <- c('Lysa', 'Petyr')
nodes_subb[nodes_subb$Label %in% arryn_mems, 'arryn'] <- 1
nodes_subb[nodes_subb$Label %in% arryn_mems, 'house'] <- 'lightblue'
nodes_subb[nodes_subb$Label %in% amar, 'arryn'] <- 3

nodes_subb$greyjoy <- rep(0, 100)
grey_mems <- c('Balon', 'Euron', 'Rodrik', 'Yara', 'Theon')
nodes_subb[nodes_subb$Label %in% grey_mems, 'greyjoy'] <- 1
nodes_subb[nodes_subb$Label %in% grey_mems, 'house'] <- 'grey'

nodes_subb$tully <- rep(0, 100)
tully_mems <- c('Catelyn', 'Lysa', 'Edmure')
tukid <- c('Sansa', 'Arya', 'Rickon', 'Robb', 'Bran', 'Robin')
tumar <- c('Ned', 'Petyr')
nodes_subb[nodes_subb$Label %in% tully_mems, 'tully'] <- 1
nodes_subb[nodes_subb$Label %in% tully_mems, 'house'] <- 'brown'
nodes_subb[nodes_subb$Label %in% tukid, 'tully'] <- 2
nodes_subb[nodes_subb$Label %in% tumar, 'tully'] <- 3

nodes_subb$mormont <- rep(0, 100)
mor_mems <- c('Jeor', 'Jorah', 'Lyanna Mormont')
nodes_subb[nodes_subb$Label %in% mor_mems, 'mormont'] <- 1
nodes_subb[nodes_subb$Label %in% mor_mems, 'house'] <- 'pink'

nodes_subb$bolton <- rep(0, 100)
bol_mems <- c('Ramsey', 'Roose')
bomar <- c('Sansa')
nodes_subb[nodes_subb$Label %in% bol_mems, 'bolton'] <- 1
nodes_subb[nodes_subb$Label %in% bol_mems, 'house'] <- 'brown4'
nodes_subb[nodes_subb$Label %in% bomar, 'bolton'] <- 3

nodes_subb$martell <- rep(0, 100)
mar_mems <- c('Oberyn', 'Tyene')
mmar <- c('Ellaria')
nodes_subb[nodes_subb$Label %in% mar_mems, 'martell'] <- 1
nodes_subb[nodes_subb$Label %in% mar_mems, 'house'] <- 'darkgoldenrod'
nodes_subb[nodes_subb$Label %in% mmar, 'martell'] <- 3

nodes_subb$house <- nodes_subb$house %>% replace_na('bisque1') 
```

```{r, results='hide'}
df_sub <- edges_df
df_sub <- df_sub[df_sub$Source %in% nodes_subb$Id, ]
df_sub <- df_sub[df_sub$Target %in% nodes_subb$Id, ]
```

```{r}
library(igraph)

nodes1 <- nodes_subb$Id
gnet1 <- graph_from_data_frame(df_sub[, 1:2], vertices = nodes1, directed = FALSE)

deg3 <- degree(gnet1)
str3 <- strength(gnet1, weights = df_sub$weight)
btwn3 <- betweenness(gnet1, weights = df_sub$weight)
close3 <- closeness(gnet1, weights = df_sub$weight)
eigen3 <- eigen_centrality(gnet1, weights = df_sub$weight)$vector

(var(deg3))
(var(str3))
(var(btwn3))
(var(close3))
(var(eigen3))
```

```{r}
(mean(deg3))
(sd(deg3))
hist(deg3)
```

```{r fig2, fig.height = 4, fig.width = 4, fig.align = 'center'}
E(gnet1)$weight <- df_sub$weight
V(gnet1)$size <- str3/2
V(gnet1)$color <- nodes_subb$house

plot(gnet1, layout = layout.random,
     vertex.color = V(gnet1)$color,
     vertex.size = V(gnet1)$size,
     vertex.label.cex = 0.75,
     vertex.size = 3,
     vertex.label.color = 'black',
     edge.width = E(gnet1)$weight,
     asp = 0)
```

```{r, results='hide'}
detach('package:igraph', unload = TRUE)
```

```{r}
pnet1 <- as.network(df_sub[, 1:3],
                 matrix.type = 'edgelist',
                 directed = FALSE,
                 ignore.eval = FALSE,
                 names.eval = 'weight')
```

```{r}
(gden(pnet1, mode = 'graph', ignore.eval = FALSE))
(centralization(pnet1, degree, mode = 'graph'))
(triad.census(pnet1, mode = 'graph'))
(gtrans(pnet1, mode = 'graph', measure = 'weak', use.adjacency = TRUE))
```

\section{4a)}
```{r, results='hide'}
covdata <- nodes_subb[, 4:17]
nodecov <- list(Dead = covdata[, 1], sex = covdata[, 2], lannister = covdata[, 3], house = covdata[, 4], targaryen = covdata[, 5], stark = covdata[, 6], baratheon = covdata[, 7], tyrell = covdata[, 8], arryn = covdata[, 9], greyjoy = covdata[, 10], tully = covdata[, 11], mormont = covdata[, 12], bolton = covdata[, 13], martell = covdata[, 14])
```

```{r, results='hide'}
nodes1 <- nodes_subb$Id
gnet2 <- network(df_sub[, 1:2], vertices = nodes1, directed = FALSE, vertex.attr = nodecov[1:14], vertex.attrnames = colnames(covdata))
```

```{r}
model1 <- ergmm(gnet2 ~ edges + nodecov('lannister') + nodecov('targaryen') + nodecov('stark') + nodecov('baratheon') + nodecov('tyrell') + nodecov('arryn') + nodecov('greyjoy') + nodecov('tully') + nodecov('mormont') + nodecov('bolton') + nodecov('martell'))
summary(model1)
```

```{r fig.height = 4, fig.width = 4, fig.align = 'center', message=FALSE}
model1_gof <- gof(model1, GOF = ~ c(degree, distance), control = control.gof.formula(nsim = 100), verbose = T)
(model1_gof)
plot(model1_gof)
```

```{r, results='hide'}
#mcmc.diagnostics(model1)
```
Chain 1 
Lag 0 
                 lpY      beta.1       beta.2      beta.3       beta.4       beta.5       beta.6       beta.7      beta.8
lpY      1.000000000  0.03509861 -0.002896724 -0.02026923 -0.007494639  0.048258569  0.020939973 -0.008996874 -0.03339938
beta.1   0.035098612  1.00000000 -0.174031037 -0.27182522 -0.270225636 -0.147814464 -0.208379189 -0.108163852 -0.30465489
beta.2  -0.002896724 -0.17403104  1.000000000  0.07291456 -0.048662741 -0.516674927 -0.131223591  0.021942514  0.02735275
beta.3  -0.020269234 -0.27182522  0.072914562  1.00000000 -0.035868054 -0.033040390  0.033314187  0.055836678  0.07220770
beta.4  -0.007494639 -0.27022564 -0.048662741 -0.03586805  1.000000000  0.052173492  0.060742562  0.263865789  0.08598837
beta.5   0.048258569 -0.14781446 -0.516674927 -0.03304039  0.052173492  1.000000000 -0.146605313  0.004400144  0.03657326
beta.6   0.020939973 -0.20837919 -0.131223591  0.03331419  0.060742562 -0.146605313  1.000000000  0.024059101  0.04476724
beta.7  -0.008996874 -0.10816385  0.021942514  0.05583668  0.263865789  0.004400144  0.024059101  1.000000000  0.03310605
beta.8  -0.033399380 -0.30465489  0.027352747  0.07220770  0.085988375  0.036573260  0.044767236  0.033106053  1.00000000
beta.9  -0.020088697 -0.20374071  0.018608046  0.04570717 -0.341287851  0.034967620  0.007795883 -0.577790712  0.03382703
beta.10  0.007827364 -0.24475947  0.020138023  0.06125715  0.066450944  0.042535197  0.011445984 -0.001472729  0.06340558
beta.11  0.021784463  0.02410319 -0.377645814 -0.06609476  0.035527190  0.180720316  0.053238876  0.167493777 -0.03904548
beta.12 -0.032270596 -0.22301726  0.028882938  0.03666473  0.036292571  0.046530829  0.017469490  0.043435469  0.06024210
              beta.9      beta.10      beta.11      beta.12
lpY     -0.020088697  0.007827364  0.021784463 -0.032270596
beta.1  -0.203740706 -0.244759467  0.024103194 -0.223017260
beta.2   0.018608046  0.020138023 -0.377645814  0.028882938
beta.3   0.045707166  0.061257149 -0.066094761  0.036664733
beta.4  -0.341287851  0.066450944  0.035527190  0.036292571
beta.5   0.034967620  0.042535197  0.180720316  0.046530829
beta.6   0.007795883  0.011445984  0.053238876  0.017469490
beta.7  -0.577790712 -0.001472729  0.167493777  0.043435469
beta.8   0.033827025  0.063405582 -0.039045478  0.060242101
beta.9   1.000000000  0.017495661 -0.250238133  0.043078246
beta.10  0.017495661  1.000000000  0.017016315  0.048901386
beta.11 -0.250238133  0.017016315  1.000000000 -0.008485722
beta.12  0.043078246  0.048901386 -0.008485722  1.000000000

Lag 10 
                  lpY      beta.1        beta.2       beta.3       beta.4      beta.5       beta.6       beta.7       beta.8
lpY      0.7072798502  0.02011194  0.0007892223 -0.026559377  0.003675086  0.04863217  0.031147209 -0.025216259 -0.018104899
beta.1   0.0397033746  0.53070361 -0.1011863535 -0.150007139 -0.205418180 -0.10986740 -0.046191181 -0.067800135 -0.175025256
beta.2  -0.0024406940 -0.12224692  0.7169089897  0.097639944 -0.034400073 -0.35965104 -0.081798216  0.011929491  0.014939266
beta.3  -0.0170671760 -0.16543521  0.0828277787  0.796368174 -0.001307246 -0.03168141 -0.023657230  0.053336482  0.033945627
beta.4   0.0052148467 -0.19881859 -0.0111345349 -0.046792315  0.692490469  0.04455564  0.049071726  0.171645729  0.060940527
beta.5   0.0479717820 -0.09156124 -0.3692292463 -0.065680746  0.061475055  0.70177419 -0.074731848  0.034804827  0.024308147
beta.6   0.0147674002 -0.01648507 -0.1212752977 -0.009984857  0.060860374 -0.08309609  0.399900847  0.008135909  0.007696193
beta.7   0.0056595677 -0.07199366  0.0411265200  0.033609370  0.185985291  0.02631012  0.011348944  0.749819436  0.032716304
beta.8  -0.0234912020 -0.18290128  0.0316411327  0.034668880  0.047675173  0.02247681  0.022123962  0.021917194  0.637294096
beta.9  -0.0251608346 -0.09167669 -0.0346171455  0.009527045 -0.192122246  0.02735043 -0.044507539 -0.383783410  0.018706433
beta.10 -0.0002311235 -0.21394761  0.0376087097  0.015036291  0.053299629  0.04192694  0.004828716  0.001091106  0.116179061
beta.11  0.0083949355  0.02024120 -0.2750816683 -0.076148417  0.042533956  0.14386726  0.010855448  0.117434898 -0.042124682
beta.12 -0.0083745958 -0.09983113  0.0148958149  0.007946289 -0.018572722  0.05869586 -0.076062665  0.009348204  0.086988635
               beta.9      beta.10       beta.11      beta.12
lpY     -0.0157123103 -0.005721428  0.0175869845 -0.027673476
beta.1  -0.1106270533 -0.204271720  0.0185387739 -0.096889315
beta.2   0.0244856780  0.033870377 -0.2760806810  0.042087248
beta.3  -0.0089673568  0.014442005 -0.0607018340  0.002808598
beta.4  -0.1911851229  0.032955284  0.0390504930 -0.022888257
beta.5   0.0007270967  0.057167608  0.1591628439  0.051181394
beta.6  -0.0555554349  0.015679911  0.0130471678 -0.047994851
beta.7  -0.3726515324 -0.019832787  0.1032559709 -0.018721698
beta.8   0.0418767894  0.082716400 -0.0756020240  0.069058736
beta.9   0.5256900288  0.070301758 -0.1493455259  0.057132101
beta.10  0.0382493157  0.697963749  0.0008117536  0.044609345
beta.11 -0.1788124960 -0.013448456  0.7452466394 -0.006660150
beta.12  0.0589995708  0.061063006  0.0061135775  0.365978954

[[1]]

Quantile (q) = 0.025
Accuracy (r) = +/- 0.0125
Probability (s) = 0.95 
                                               
         Burn-in  Total Lower bound  Dependence
         (M)      (N)   (Nmin)       factor (I)
 lpY     80       13570 600          22.6      
 beta.1  50       9860  600          16.4      
 beta.2  80       14240 600          23.7      
 beta.3  80       14240 600          23.7      
 beta.4  120      21540 600          35.9      
 beta.5  80       13250 600          22.1      
 beta.6  50       10070 600          16.8      
 beta.7  100      16920 600          28.2      
 beta.8  80       16800 600          28.0      
 beta.9  60       14100 600          23.5      
 beta.10 70       12630 600          21.0      
 beta.11 100      16660 600          27.8      
 beta.12 40       7800  600          13.0      

```{r, results='hide'}
nodecov$blan <- ifelse(nodecov$lannister >= 1, 1, 0)
nodecov$btar <- ifelse(nodecov$targaryen >= 1, 1, 0)
nodecov$bstar <- ifelse(nodecov$stark >= 1, 1, 0)
nodecov$bbar <- ifelse(nodecov$baratheon >= 1, 1, 0)
nodecov$btyr <- ifelse(nodecov$tyrell >= 1, 1, 0)
nodecov$barr <- ifelse(nodecov$arryn >= 1, 1, 0)
nodecov$bgrey <- ifelse(nodecov$greyjoy >= 1, 1, 0)
nodecov$btul <- ifelse(nodecov$tully >= 1, 1, 0)
nodecov$bmor <- ifelse(nodecov$mormont >= 1, 1, 0)
nodecov$bbol <- ifelse(nodecov$bolton >= 1, 1, 0)
nodecov$bmar <- ifelse(nodecov$martell >= 1, 1, 0)
nodecov$bsex <- nodecov$sex

gnet3 <- network(df_sub[, 1:2], vertices = nodes1, directed = FALSE, vertex.attr = nodecov[15:26], vertex.attrnames = c('blan', 'btar', 'bstar', 'bbar', 'btyr', 'barr', 'bgrey', 'btul', 'bmor', 'bbol', 'bmar', 'sex' ))
```

```{r}
model2 <- ergmm(gnet3 ~ edges + nodecov('blan') + nodecov('btar') + nodecov('bstar') + nodecov('bbar') + nodecov('btyr') + nodecov('barr') + nodecov('bgrey') + nodecov('btul') + nodecov('bmor') + nodecov('bbol') + nodecov('bmar'))

summary(model2)
```

```{r fig.height = 4, fig.width = 4, fig.align = 'center', message=FALSE}
model2_gof <- gof(model2, GOF = ~ c(degree, distance), control = control.gof.formula(nsim = 100), verbose = T)
(model2_gof)
plot(model2_gof)
```

```{r, results='hide'}
#mcmc.diagnostics(model2)
```
Chain 1 
Lag 0 
                 lpY       beta.1       beta.2      beta.3       beta.4       beta.5       beta.6       beta.7       beta.8
lpY      1.000000000  0.004841970 -0.003701243 -0.07676081  0.005014860 -0.068515037  0.046111662 -0.002753561  0.015567137
beta.1   0.004841970  1.000000000 -0.159251062 -0.34442227 -0.135981358 -0.172549513 -0.221081874 -0.093399173 -0.314065972
beta.2  -0.003701243 -0.159251062  1.000000000  0.04897044 -0.124167682 -0.539089529 -0.008293759 -0.043341761  0.045165723
beta.3  -0.076760810 -0.344422273  0.048970443  1.00000000 -0.207442825  0.040420956  0.041045323 -0.088657413  0.103541421
beta.4   0.005014860 -0.135981358 -0.124167682 -0.20744282  1.000000000  0.050645636  0.044521632  0.555198592  0.001933211
beta.5  -0.068515037 -0.172549513 -0.539089529  0.04042096  0.050645636  1.000000000 -0.266764516  0.025036980  0.034043166
beta.6   0.046111662 -0.221081874 -0.008293759  0.04104532  0.044521632 -0.266764516  1.000000000  0.008480807  0.035684326
beta.7  -0.002753561 -0.093399173 -0.043341761 -0.08865741  0.555198592  0.025036980  0.008480807  1.000000000  0.021548208
beta.8   0.015567137 -0.314065972  0.045165723  0.10354142  0.001933211  0.034043166  0.035684326  0.021548208  1.000000000
beta.9   0.004548420 -0.154177790  0.066378371  0.20321581 -0.717528189  0.019900863  0.017398076 -0.713409635  0.066949671
beta.10  0.029680896 -0.287587330  0.002531658  0.06361776  0.013080290  0.070849846  0.051183008 -0.024302118  0.051799307
beta.11  0.011132792  0.003197763 -0.211155153 -0.03952573 -0.006350251  0.134049873  0.022017280  0.058359193 -0.007752978
beta.12  0.031199589 -0.293532901  0.021444639  0.08341868 -0.003058642  0.008465907  0.060969947  0.018464967  0.082695332
             beta.9      beta.10      beta.11      beta.12
lpY      0.00454842  0.029680896  0.011132792  0.031199589
beta.1  -0.15417779 -0.287587330  0.003197763 -0.293532901
beta.2   0.06637837  0.002531658 -0.211155153  0.021444639
beta.3   0.20321581  0.063617763 -0.039525725  0.083418676
beta.4  -0.71752819  0.013080290 -0.006350251 -0.003058642
beta.5   0.01990086  0.070849846  0.134049873  0.008465907
beta.6   0.01739808  0.051183008  0.022017280  0.060969947
beta.7  -0.71340963 -0.024302118  0.058359193  0.018464967
beta.8   0.06694967  0.051799307 -0.007752978  0.082695332
beta.9   1.00000000  0.089209032 -0.133915704  0.065314975
beta.10  0.08920903  1.000000000 -0.033283555  0.049473707
beta.11 -0.13391570 -0.033283555  1.000000000  0.016047410
beta.12  0.06531498  0.049473707  0.016047410  1.000000000

Lag 10 
                 lpY       beta.1        beta.2      beta.3       beta.4       beta.5      beta.6        beta.7       beta.8
lpY      0.651214716  0.005811914  0.0060301206 -0.06665700 -0.003973962 -0.075550009  0.04520400 -0.0009717712  0.016740657
beta.1   0.028255720  0.453003091 -0.0684228375 -0.18752123 -0.100165105 -0.122458967 -0.13905149 -0.0529220600 -0.086161606
beta.2   0.002763231 -0.091727533  0.7965101921  0.03859868 -0.061626680 -0.438224207 -0.01304464 -0.0058931860  0.017622654
beta.3  -0.077980063 -0.199847645  0.0224217044  0.74607651 -0.185999780  0.033497730  0.03418118 -0.0605353474  0.035072920
beta.4   0.015602215 -0.112147245 -0.0659222055 -0.18514211  0.781708884  0.032049317  0.07262053  0.3654182486  0.042842097
beta.5  -0.072852533 -0.099678311 -0.4292124870  0.02755238  0.016753066  0.740045275 -0.12246672  0.0016956551  0.004583273
beta.6   0.038741343 -0.122195585 -0.0039623539  0.03032727  0.050866623 -0.146900632  0.44908613  0.0273383728  0.050623751
beta.7  -0.002924945 -0.065858056 -0.0004513025 -0.06995303  0.385896610 -0.003854676  0.03431010  0.5497158537  0.052067591
beta.8   0.012522508 -0.085450645  0.0064448690  0.05190060  0.050681282  0.018061137  0.02692326  0.0452735910  0.475563848
beta.9  -0.002615042 -0.062001947  0.0027070773  0.15675368 -0.542771946  0.046640291 -0.04765133 -0.4566314152 -0.014528015
beta.10  0.017058928 -0.167648260  0.0226087562  0.02513348  0.009415247  0.047924611  0.06159591  0.0012382874 -0.021871137
beta.11  0.001201902 -0.040209756 -0.1513286247 -0.01471108 -0.007051779  0.077148311  0.06721537  0.0316555141 -0.051153312
beta.12  0.037945918 -0.179995102  0.0136378715  0.06285229 -0.028918201  0.015045497  0.01863088  0.0001757116  0.047002280
             beta.9      beta.10      beta.11       beta.12
lpY      0.01168262  0.030181151 -0.005469342  0.0325503149
beta.1  -0.07087780 -0.188814037 -0.050778430 -0.2152729038
beta.2   0.01678235  0.037598710 -0.170875653  0.0097554447
beta.3   0.16340521  0.056781710 -0.016078073  0.0648997433
beta.4  -0.54362868  0.003375293  0.001215629 -0.0063100884
beta.5   0.03278964  0.023517902  0.098757296  0.0205891159
beta.6  -0.03795494  0.043815809  0.054077024  0.0174921476
beta.7  -0.47256593  0.002389782  0.038003561 -0.0005381706
beta.8  -0.01183412 -0.018821663 -0.057587566  0.0641341367
beta.9   0.71569627  0.060267889 -0.061250698  0.0576151644
beta.10  0.05380093  0.623424013 -0.056443543  0.0877301568
beta.11 -0.04928348 -0.077529255  0.607874248  0.0789294246
beta.12  0.05710569  0.103917792  0.092035457  0.6004688350

[[1]]

Quantile (q) = 0.025
Accuracy (r) = +/- 0.0125
Probability (s) = 0.95 
                                               
         Burn-in  Total Lower bound  Dependence
         (M)      (N)   (Nmin)       factor (I)
 lpY     100      21000 600          35.0      
 beta.1  40       7800  600          13.0      
 beta.2  80       14600 600          24.3      
 beta.3  80       14600 600          24.3      
 beta.4  80       14240 600          23.7      
 beta.5  80       13570 600          22.6      
 beta.6  40       8480  600          14.1      
 beta.7  50       9650  600          16.1      
 beta.8  80       14900 600          24.8      
 beta.9  80       14180 600          23.6      
 beta.10 70       12060 600          20.1      
 beta.11 60       11520 600          19.2      
 beta.12 80       13250 600          22.1      

Are women more likely to connect to people, are they more likely to connect to other women specifically.
```{r}
model3 <- ergmm(gnet3 ~ edges + nodematch('sex', diff = FALSE) + nodecov('blan') + nodecov('btar') + nodecov('bstar') + nodecov('bbar') + nodecov('btyr') + nodecov('barr') + nodecov('bgrey') + nodecov('btul') + nodecov('bmor') + nodecov('bbol') + nodecov('bmar'))
summary(model3)
```

```{r fig.height = 4, fig.width = 4, fig.align = 'center', message=FALSE}
model3_gof <- gof(model3, GOF = ~ c(degree, distance), control = control.gof.formula(nsim = 100), verbose = T)
(model3_gof)
plot(model3_gof)
```

```{r, results='hide'}
#mcmc.diagnostics(model3)
```
Chain 1 
Lag 0 
                  lpY      beta.1        beta.2        beta.3        beta.4      beta.5       beta.6       beta.7       beta.8
lpY      1.0000000000  0.02884424 -0.0417985297  0.0005281698 -0.0041459989 -0.03127554 -0.015885908  0.048862032 -0.033272001
beta.1   0.0288442440  1.00000000 -0.6712046612 -0.1150188658 -0.2088219152 -0.11198637 -0.222923304 -0.162295298 -0.097638772
beta.2  -0.0417985297 -0.67120466  1.0000000000 -0.0325947396 -0.0002255248 -0.01602242  0.082882938  0.020005642 -0.007576977
beta.3   0.0005281698 -0.11501887 -0.0325947396  1.0000000000  0.1220835949 -0.17833780 -0.528050836  0.029707890 -0.051139002
beta.4  -0.0041459989 -0.20882192 -0.0002255248  0.1220835949  1.0000000000 -0.20174786  0.001099503  0.056307004 -0.085178790
beta.5  -0.0312755408 -0.11198637 -0.0160224158 -0.1783377981 -0.2017478584  1.00000000  0.156461793 -0.026987968  0.539471403
beta.6  -0.0158859082 -0.22292330  0.0828829377 -0.5280508362  0.0010995032  0.15646179  1.000000000 -0.251602127  0.064660030
beta.7   0.0488620323 -0.16229530  0.0200056422  0.0297078905  0.0563070041 -0.02698797 -0.251602127  1.000000000 -0.008548124
beta.8  -0.0332720013 -0.09763877 -0.0075769767 -0.0511390020 -0.0851787902  0.53947140  0.064660030 -0.008548124  1.000000000
beta.9  -0.0063125253 -0.28022625  0.0241001954 -0.0074292176  0.1094312797  0.07202511  0.133918938  0.002063931  0.065184013
beta.10  0.0572389399 -0.13429064  0.0639516286  0.1291888102  0.1871775994 -0.69887660 -0.051686613  0.069690690 -0.705763277
beta.11  0.0076087169 -0.21818463  0.0205982894  0.0049834421  0.0402378011  0.03687967  0.067192465 -0.014041003  0.046987024
beta.12  0.0039833375 -0.05312534  0.0119324991 -0.2252378512  0.0056897117  0.02596852  0.102664862  0.001455794  0.136967809
beta.13 -0.0414479000 -0.26885041  0.1112763774  0.0383617151  0.0377286552 -0.02239125  0.064754853  0.041570801  0.016321480
              beta.9      beta.10      beta.11      beta.12     beta.13
lpY     -0.006312525  0.057238940  0.007608717  0.003983338 -0.04144790
beta.1  -0.280226251 -0.134290642 -0.218184625 -0.053125342 -0.26885041
beta.2   0.024100195  0.063951629  0.020598289  0.011932499  0.11127638
beta.3  -0.007429218  0.129188810  0.004983442 -0.225237851  0.03836172
beta.4   0.109431280  0.187177599  0.040237801  0.005689712  0.03772866
beta.5   0.072025115 -0.698876601  0.036879667  0.025968522 -0.02239125
beta.6   0.133918938 -0.051686613  0.067192465  0.102664862  0.06475485
beta.7   0.002063931  0.069690690 -0.014041003  0.001455794  0.04157080
beta.8   0.065184013 -0.705763277  0.046987024  0.136967809  0.01632148
beta.9   1.000000000  0.001689467  0.041515464 -0.034202289  0.08567241
beta.10  0.001689467  1.000000000  0.017954872 -0.157763732  0.05295690
beta.11  0.041515464  0.017954872  1.000000000  0.028435661  0.06112644
beta.12 -0.034202289 -0.157763732  0.028435661  1.000000000 -0.01926311
beta.13  0.085672408  0.052956899  0.061126440 -0.019263106  1.00000000

Lag 10 
                  lpY      beta.1       beta.2        beta.3       beta.4        beta.5      beta.6      beta.7        beta.8
lpY      0.6877214585  0.02265456 -0.040246493  7.680412e-05  0.014422056 -0.0412136335 -0.01264036  0.04325156  0.0009700344
beta.1   0.0293550339  0.87133944 -0.591017486 -1.104950e-01 -0.149964661 -0.0944480781 -0.20943641 -0.11432884 -0.0699143877
beta.2  -0.0384936286 -0.57494774  0.808029004  7.756049e-03 -0.007456244 -0.0054895442  0.07523831  0.02735701  0.0093057219
beta.3   0.0035178826 -0.11213361 -0.005771968  8.367183e-01  0.102393569 -0.1757571748 -0.45914098  0.00515087 -0.0344304497
beta.4  -0.0160834591 -0.15753203 -0.003000052  1.310008e-01  0.632256649 -0.0492163104 -0.03867682  0.09010756 -0.0237377854
beta.5  -0.0205176680 -0.10080328 -0.005718977 -1.987447e-01 -0.043766231  0.6599587169  0.17527167 -0.07607020  0.2914199535
beta.6  -0.0161169064 -0.19388110  0.086727022 -4.717807e-01 -0.040389473  0.1723168140  0.86734069 -0.20889181  0.0834715118
beta.7   0.0644794237 -0.12773898  0.019412493 -1.474886e-03  0.103804404 -0.0802176756 -0.18382208  0.67664257 -0.1227241692
beta.8  -0.0175263357 -0.07411023 -0.010525408 -5.934584e-02 -0.033438772  0.3083621308  0.10130812 -0.10691801  0.2652211275
beta.9  -0.0009886078 -0.25374473  0.036166644 -4.826769e-02  0.086390457  0.0892837201  0.17192606 -0.02782799  0.0394687051
beta.10  0.0399218734 -0.11339006  0.084082829  1.415609e-01  0.033624263 -0.3916349275 -0.07221386  0.12655947 -0.2520756303
beta.11  0.0057493954 -0.17923197  0.063354042 -1.269550e-02 -0.009817945  0.0007567698  0.05306506 -0.01336931 -0.0265545615
beta.12 -0.0035299814 -0.05780300  0.008744552 -1.884709e-01 -0.005599604  0.0260738387  0.07888415  0.03985163  0.1139442046
beta.13 -0.0306628852 -0.23180916  0.106026699  2.387439e-02  0.047312508 -0.0149309745  0.02529168  0.05072115  0.0344040143
              beta.9      beta.10     beta.11      beta.12      beta.13
lpY      0.008110439  0.045326604  0.01829181  0.016328795 -0.027524115
beta.1  -0.239600170 -0.111871053 -0.17589065 -0.055028758 -0.245438183
beta.2   0.017692617  0.059962664  0.04849385 -0.007366211  0.125014309
beta.3  -0.046991778  0.130204063  0.01758764 -0.196971869  0.035023802
beta.4   0.090128172  0.034129310 -0.03561989 -0.016669632  0.071358468
beta.5   0.083069260 -0.378906067  0.01490910  0.037419040 -0.007152710
beta.6   0.148077163 -0.074203760  0.03531941  0.098331728  0.027946362
beta.7  -0.016422657  0.146401689 -0.01721832  0.040119397  0.062318626
beta.8   0.042429109 -0.238282251 -0.01462313  0.114551685  0.041747274
beta.9   0.815814646 -0.027619529  0.05744766 -0.039958146  0.063157083
beta.10 -0.023197162  0.410701406  0.02516120 -0.119302604 -0.005924339
beta.11  0.059590146  0.042364996  0.65476234  0.062702664  0.053671580
beta.12 -0.042072017 -0.127512234  0.05119111  0.881794616 -0.016586946
beta.13  0.070351619 -0.002295061  0.05615156 -0.004595329  0.740274306

[[1]]

Quantile (q) = 0.025
Accuracy (r) = +/- 0.0125
Probability (s) = 0.95 
                                               
         Burn-in  Total Lower bound  Dependence
         (M)      (N)   (Nmin)       factor (I)
 lpY     80       13690 600          22.8      
 beta.1  220      39920 600          66.5      
 beta.2  180      29960 600          49.9      
 beta.3  160      31060 600          51.8      
 beta.4  50       9860  600          16.4      
 beta.5  60       11520 600          19.2      
 beta.6  160      28400 600          47.3      
 beta.7  90       14970 600          25.0      
 beta.8  20       6210  600          10.4      
 beta.9  100      16940 600          28.2      
 beta.10 30       7170  600          12.0      
 beta.11 60       11110 600          18.5      
 beta.12 180      35130 600          58.6      
 beta.13 70       12630 600          21.0      
